%-------------------------
% Resume in Latex
% Author : Jacob Sansbury
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://workbyjacob.com/}{\Large Jacob Sansbury}} & Email : \href{mailto:me@workbyjacob.com}{me@workbyjacob.com}\\
  \href{http://workbyjacob.com/}{workbyjacob.com} & Mobile : +1-803-445-3351 \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Bridgewater Associates}{Westport, CT}
      {Security Engineer}{June 2018 - Present}
      \resumeItemListStart
        \resumeItem{Iris}
          {Iris is an internal graph analysis tool specifically designed for incident response and insider-threat investigation workflows.}
          \begin{itemize}
          	\item Shadowed customers to build and prioritize requirements
			\item Developed a scalable application utilizing GraphQL and React
			\item Designed highly available and fault tolerant AWS infrastructure
			\item Built Terraform to automate deployment of AWS resources
          \end{itemize}
        \resumeItem{Policy DB}
          {is a proxy policy configuration engine designed to track the lifecycle of a policy exception and enforce configuration across multiple proxy providers.}
      \resumeItemListEnd

	\resumeSubheading
		{Sansbury Consulting}{Tampa, FL}
		{Application Engineering}{October 2017 - June 2018}
		\resumeItemListStart
			\resumeItem{Mad Mobile Concierge}
				{Concierge is a leading MPOS solution used globally by Brooks Brothers, Vans, and The North Face.}
				\begin{itemize}
					\item Developed GDPR compliant analytics system
					\item Lead adoption of test driven development to slash regression rates across all company applications
				\end{itemize}
			\resumeItem{ID Plans Remote Property Manager}
				{Remote Property Manager is a real estate management system used by property managers nationwide.}
				\begin{itemize}
					\item Achieved plan load time performance improvements of 2X
					\item Migrated on-premise infrastructure to AWS
				\end{itemize}
		\resumeItemListEnd

	\resumeSubheading
		{SentinelSix}{Columbia, SC}
		{Full Stack Engineer}{June 2017 - October 2017}
		\resumeItemListStart
			\resumeItem{Guardian Angel}{Guardian Angel is a global personnel security solution adopted by multiple Fortune 100 companies}
			\begin{itemize}
             \item Implemented CI/CD pipeline with Docker Cloud and Jenkins
             \item Built React-based real-time tracking dashboard and multi-tenant user management system.
             \item Developed native iOS application
             \item Built performant geospatial data ingestion endpoints, using Go.
             \item Designed and implemented plugin management solutions to cut Webpack build times.
             \item Slashed technical debt through preventive code review strategies and cut cloud costs through datastore index optimization strategies.
             \item Recruited and hired emerging developers through outreach to local high schools, hiring 3 interns.
            \end{itemize}
		\resumeItemListEnd

\resumeSubheading
		{TCube Solutions}{Columbia, SC}
		{Software Application Developer}{April 2016 - June 2017}
		\resumeItemListStart
    		\resumeItem{R\&D}{I developed and implemented business solutions and applications, while playing integral role in researching and recommending new technologies for the insurance sector. Part of this process was developing cost / benefit analyses and demonstrations.}
			\begin{itemize}
                \item Spearheaded research and development of use cases for potential use of blockchain technologies in the insurance sector.
                \item Drove automation of project kickoff and task assignment processes using JIRA.
                \item Launched internal file sharing tool to enable storage / sharing of 500 files per week.
            \end{itemize}
		\resumeItemListEnd


	\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Personal Finance Toolkit}
      {Personal finance data generation and exploration toolkit codifying my decision making logic for more accurate decision making.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
